%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
  {Senior Backend \& Smart Contracts Engineer} % Job title
  {\href{https://blockapex.io/}{BlockApex}} % Organization
  {Karachi, pk} % Location
  {Aug. 2024 - Present{\enskip\cdotp\enskip}1.5 yr+} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Led a lean team to build a cross-chain heterogenous \strong{yield aggregator} producing 8\%+ stablecoin APY with \strong{100\% test covered} backend services, smart contracts and graph indexers.}
      \item {Contributed 5+ libraries to \href{https://github.com/timewave-computer/valence-protocol/pull/437}{\textcolor{awesome}{valence-protocol}} and long awaited \href{https://github.com/blockcoders/nestjs-ethers/pull/168}{\textcolor{awesome}{upgrade}} to a package with \strong{1000+ weekly downloads.}}
      \item {Ranked 6th for reporting a high severity vulnerability in a \href{https://cantina.xyz/code/e9e9b3e0-f213-45e4-8d05-d72bf0c8787a/overview/leaderboard}{\textcolor{awesome}{public security contest}} held on Cantina.}
      \item {Co-audited a protocol on \strong{TON Blockchain} reporting several critical vulnerabilities and proposing actionable remedies.}
      \item {Authored and reviewed technical architecture sections for multiple AI × Blockchain project proposals}
      \item {Published \strong{3 technical blog posts} on \href{https://mmujtabaroohani.medium.com/pure-unit-testing-func-smart-contract-7a5dda2e6a3b}{smart contract testing} and \href{https://blockapex.io/building-a-yield-aggregator/}{yield aggregator design}, sharing original insights with the Web3 community.}
    \end{cvitems}
  }

  \cventry
  {Software Engineer II} % Job title
  {\href{https://sadapay.pk/}{SadaPay Technologies Ltd.}} % Organization
  {Dubai, UAE} % Location
  {Oct. 2023 - Jul. 2024{\enskip\cdotp\enskip}9 mo} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Collaborated in \strong{mob-programming} sessions with highly talented colleagues, fostering collaboration and ensuring shared code ownership.}
      \item {Focused on Backend services written with \strong{Kotlin} and \strong{Springboot}, engaging in chapter meetings, proposing and discussing ideas to improve resilience of our backend services.}
      \item {Investigated and resolved 150\% increased API time-consumption post-service-upgrade by identifying and fixing a critical bug, testing in staging and production, and sharing the solution with the broader team. Received \strong{public praise} for the same.}
      \item {Identified and corrected CI/CD GitHub workflow issues to \strong{prevent unintended code releases.}}
      \item {Enhanced monitoring dashboards on Kibana and Dynatrace for proactive service performance monitoring.}
      \item {Investigated and resolved issues to improve service availability from 99.8\% to 99.98\%.}
      \item {Practiced \strong{Test-Driven Development (TDD)} to create and maintain 98\% covered services and apps producing highly reliable software for our customers.}
      \item {Contributed to building and delivering a fully functional Ledger from scratch, including inter-service APIs, an iOS widget for displaying balance, and a control module in the admin portal. Actively involved in backend development, iOS widget support, and web module extraction.}
      \item {Owned the generation of `Account Statement' feature starting from the SPIKE ticket to monitoring the post-production performance.}
      \item {Participated responsibly in on-call rotations, which included reacting to incidents, reducing alert noise, and ensuring a healthy system state.}
    \end{cvitems}
  }
      
  %---------------------------------------------------------
  \cventry
  {Backend Software Engineer (NodeJS)} % Job title
  {\href{https://www.tilismtech.com/}{Tilism Technologies}} % Organization
  {Karachi, Pakistan} % Location
  {Jan. 2023 - Oct. 2023{\enskip\cdotp\enskip}8 mo} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Led a team of 6 engineers, enhancing an embedded chat framework for businesses.}
      \item {Managed and extended on-premise Kubernetes cluster and improved CI/CD workflows.}
      \item {Made public contribution with a module for \href{https://github.com/processone/ejabberd-contrib/pull/311}{\textcolor{awesome}{ejabberd}} in \strong{Erlang}, and helped the company adopt it saving \strong{9000 USD} annually}
      \item {Helped the company swiftly shift focus to their B2B model by reusing their existing infrastructure advancement from their flagship product.}
    \end{cvitems}
  }

  \cventry
  {iOS Engineer} % Job title
  {} % Organization
  {} % Location
  {Nov. 2020 - Jan. 2023{\enskip\cdotp\enskip}2 yr 3 mo} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Led a team of 3 iOS engineers, fostering a sense of shared responsibility among them, and maintained a culture of reviewing each other's work and engage in productive discussions to write better code each day.}
      \item {Maintained and extended a hyper-localised, integrated social media and messaging application used by over a million users.}
      \item {Identified and implemented various \strong{XMPP} extensions introducing exciting features for our users.}
      \item {Devised a framework for \strong{Clean Architecture} and migrated $\sim$40\% of the code base to it achieving partial testability.}
      \item {Got recognition for my cross-domain problem-solving skills with an early promotion.}
    \end{cvitems}
  }

  \cventry
  {Consultant (Ongoing)} % Job title
  {}
  {}
  {Oct. 2023 - Present{\enskip\cdotp\enskip}1 y+} % Date(s)
  {
  }

%---------------------------------------------------------
  \cventry
  {Founding member \& iOS + Backend engineer} % Job title
  {Technollage} % Organization
  {Karachi, Pakistan} % Location
  {Nov. 2015 - Aug. 2019{\enskip\cdotp\enskip}3 yr 8 mo} % Date(s)
  {
  }

%---------------------------------------------------------
\end{cventries}
